---
title: "Update package"
format: html
editor: visual
---

## Update albert package

```{r}
library(devtools)
library(roxygen2)

getwd() #should be the albert directory if project is open
```

The first bit of code is necessary to create the package initially. It is not necessary to run it again.

```{r}
#setwd("C:/Users/NAIM001/Hennepin County/Public Health Data - Documents/Informatics/Github/HennepinCountyPublicHealth/")
#create("albert")
```

First, add new functions to the R folder. Use this script to update package documentation when new functions are added. See the existing functions for examples of how functions should be formatted. There's probably a newer or more complex way to do this, but this works just fine for us.

```{r}
document()
```

Once the documentation has been updated, push the local changes to Github. See the Github manual for further information. The updated package can be downloaded using `devtools::install_github("HennepinCountyPublicHealth/albert")`.

In addition to adding function, we may occasionally add data to the package review the steps in the 'Add data' notebook if you wish to do that as well.
